Hydrodynamics of a Semipermeable Vesicle Under Flow and Confinement

### 2020-12-30 vesicle_code/docs/permeableVes/main.tex
fixed figures 6 and 7 pdf versions

\section*{Supplementary Material: Formulation}
We consider a two-dimensional inextensible semipermeable vesicle,
$\gamma$, suspended in unconfined and confined geometries $\Omega$. The
vesicle is parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is
time. The suspending fluid is assumed to be viscous so that the fluid
velocity $\uu$ and pressure $p$ are governed by the incompressible
Stokes equations
\begin{align}
  \label{eqn:governing}
  -\nabla p + \mu \triangle \uu = 0, \quad
  \nabla \cdot \uu = 0, \qquad \xx \in \Omega \setminus \gamma,
\end{align}
where $\mu$ is the fluid viscosity. In an unconfined geometry, the
condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $|\xx|
\rightarrow \infty$, and in a confined geometry, the boundary condition
$\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
is prescribed. Along the vesicle $\gamma$, mass continuity, force
balance, and local inextensibility are enforced by requiring
\begin{align}
  \label{eqn:jump}
  \jump{\uu} = 0, \quad
  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
  \xx_s \cdot \uu_s = 0,
\end{align}
where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
jump across the interface, and $T$ is the hydrodynamic stress tensor.
The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
with bending modulus $k_b$ and a force due to the tension $\Lambda$.
Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
= \Lambda - 1.5\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
the bending and tension forces are $\ff_\mathrm{ben} = -k_b \xx_{ssss}$
and $\ff_\mathrm{ten} = (\sigma \xx_s)_s$.

@@

The governing equations are non-dimensionalized by introducing a length
scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
variable in vesicle suspensions is the reduced area $\nu = 4\pi A/L^2
\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
length is conserved by the local inextensibility condition, but the area
is not because of semipermeability. Therefore, the reduced area is
dynamic.

>>>>

\section*{Supplementary Material: Formulation}
We consider a two-dimensional inextensible semipermeable vesicle,
$\gamma$, suspended in unconfined and confined geometries $\Omega$. The
vesicle is parameterized as $\xx(s,t)$ where $s$ is arclength and $t$ is
time. The suspending fluid is assumed to be viscous so that the fluid
velocity $\uu$ and pressure $p$ are governed by the incompressible
Stokes equations
\begin{align}
  \label{eqn:governing}
  -\nabla p + \mu \triangle \uu = 0, \quad
  \nabla \cdot \uu = 0, \qquad \xx \in \Omega \setminus \gamma,
\end{align}
where $\mu$ is the fluid viscosity. In an unconfined geometry, the
condition $\uu(\xx) \rightarrow \uu_\infty(\xx)$ is enforced as $|\xx|
\rightarrow \infty$, and in a confined geometry, the boundary condition
$\uu(\xx) = \UU(\xx)$ is enforced on $\partial \Omega$, where $\UU(\xx)$
is prescribed. Along the vesicle, mass continuity, force balance, and
local inextensibility are enforced by requiring
\begin{align}
  \label{eqn:jump}
  \jump{\uu} = 0, \quad
  \jump{T\cdot\nn} = \ff_\mathrm{mem}, \quad
  \xx_s \cdot \uu_s = 0,
\end{align}
where $\nn$ is the outward normal of $\gamma$, $\jump{\cdot}$ is the
jump across the interface, and $T$ is the hydrodynamic stress tensor.
The membrane force $\ff_\mathrm{mem}$ is the sum of a bending force
with bending modulus $k_b$ and a force due to the tension $\Lambda$.
Following~\cite{vee-gue-zor-bir2009}, we introduce the variable $\sigma
= \Lambda - 1.5\kappa^2$, where $\kappa$ is the vesicle curvature. Then,
the bending and tension forces corresponding to the Helfrich energy are
$\ff_\mathrm{ben} = -k_b \xx_{ssss}$ and $\ff_\mathrm{ten} = (\sigma
\xx_s)_s$.

@@

The governing equations are non-dimensionalized by introducing a length
scale that we take to be $R_0 = 10^{-6}$m. Using a bending stiffness of
$k_b = 10^{-19}$J and fluid viscosity $5 \times 10^{-2}$kg/ms, we define
the time scale $\tau = \mu R_0^3/k_b = 0.5s$, the velocity scale $U =
R_0/\tau = 2\mu$m/s, the pressure scale $P = k_b/R_0^3 = 10^{-1}$Pa, the
tension scale $Q = k_b/R_0^2 = 10^{-7}$N/m, and the permeability scale
$W = R_0\mu = 2 \times 10^{-5}$m$^2$s/kg. Another standard dimensionless
variable in vesicle suspensions is the reduced area $\alpha = 4\pi A/L^2
\in (0,1]$, where $L$ is the vesicle length and $A$ is its area. The
length is conserved by the local inextensibility condition, but the area
is not because of semipermeability. Therefore, the reduced area is
dynamic.
